Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update Conclusion

## Conclusion
Considering the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization. 
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear 
dynamics analyses, our results have serious implications for monitoring global
movements in consistent across other social uprisings. While traditional, 
state-run media in regions of authoritarian rule are often biased and 
propaganda for the leader and central government, the 
self-organized nature of Twitter poses a new avenue to gain insight into 
truths about up-risings and social mobilization. By conceptualizing Twitter 
and real-world events as two elements of an inextricably linked dynamical 
system, the levels of social cohesion within social media platforms could be 
monitored for fluctuations indicating shifts in power and peace. Social media
mobilization may thus help alert the world to citizens' actions and reactions 
that are suppressed by government regimes, providing insight into events that 
may not otherwise be broadcast and allowing for faster intervention.

>>>>

## Conclusion
Considering the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization. 
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear 
dynamics analyses, our results have serious implications for monitoring global
movements in consistent across other social uprisings. While  
state-run media in regions of authoritarian rule are often biased and 
serve as propaganda for the leader and central government, the 
self-organized nature of Twitter provides a new avenue to gain insight into 
truths about uprisings and social mobilization. By conceptualizing Twitter 
and real-world events as two elements of an inextricably linked dynamical 
system, the levels of social cohesion within social media platforms could be 
monitored for fluctuations indicating shifts in power and peace. Social media
mobilization may thus help alert the world to citizens' actions and reactions 
that are suppressed by government regimes, providing insight into events that 
may not otherwise be broadcast and allowing for faster intervention.
